Climate-RWI relations

### 2018-01-25 analysis/rwi/climate_rwi_relate.Rmd
update rwi climate

```{r}
machine <- 'ajpelu'
# machine <- 'ajpeluLap'
di <- paste0('/Users/', machine, '/Dropbox/phd/phd_repos/qpyr_dendro/', sep = '')
```

@@

custom_gg <- list(theme_cor(), 
                  geom_hline(yintercept = 0, colour="gray"),
                  ylab('Correlation'), 
                  geom_bar(aes(fill=site), stat="identity", position = "dodge"),
                  geom_text(aes(label = sig, 
                                x = id, 
                                y = (coef + ifelse(coef >= 0, 0.02, -0.02))), 
                            position = position_dodge(.9), size = 10),
                  scale_fill_manual(values = c("#B2DF8A","#1F78B4","#A6CEE3")))
                  # scale_fill_brewer(palette = 'Paired', type='qual'))

@@

@@

@@

@@

>>>>

```{r}
# machine <- 'ajpelu'
machine <- 'ajpeluLap'
di <- paste0('/Users/', machine, '/Dropbox/phd/phd_repos/qpyr_dendro/', sep = '')
```

@@

custom_gg <- list(theme_cor(), 
                  geom_hline(yintercept = 0, colour="gray"),
                  ylab('Correlation'), 
                  geom_bar(aes(fill=site), stat="identity", position = "dodge"),
                  geom_text(aes(label = sig, 
                                x = id, 
                                y = (coef + ifelse(coef >= 0, 0.02, -0.02))), 
                            position = position_dodge(.9), size = 8),
                  scale_fill_manual(values = c("#B2DF8A","#1F78B4","#A6CEE3")))
                  # scale_fill_brewer(palette = 'Paired', type='qual'))

@@

rprec_all <- rprec_all %>% 
  mutate(month_name = case_when(
      month == "sep...AUG" ~ "Hydrol", 
      TRUE ~ as.character(.$month)))

write.csv(rprec_all, file=paste(di, "data/rwi_climate/rprec_selected.csv", sep=""), row.names = TRUE)
```

@@

rsequia_all <- customNames(rsequia_all) 
write.csv(rsequia_all, file=paste(di, "data/rwi_climate/rsequia_selected.csv", sep=""), row.names = TRUE)
```

@@

# Rename variable 
rtmin_all <- customNames(rtmin_all) 
write.csv(rtmin_all, file=paste(di, "data/rwi_climate/rtmin_selected.csv", sep=""), row.names = TRUE)
```

@@

# Rename variable 
rtmax_all <- customNames(rtmax_all) 
write.csv(rtmax_all, file=paste(di, "data/rwi_climate/rtmax_selected.csv", sep=""), row.names = TRUE)
```
